A new method to explicitly estimate the shift of optimum along gradients in multispecies studies

### 2023-01-03 redaction/manuscript_cut.Rmd
Shortening abstract as suggested by JoB's editor
1st sentence Abstract_conclusions remove "Our findings indicate that " and instead simply state what they imply.

### Main conclusions
Our findings indicate that EHMOS could be used for a wide range of topics and extended to produce new insights, especially in climate change studies. Explicit estimation of optimum shifts notably allows investigation of ecological assumptions that could explain interspecific variability of these shifts.

>>>>

### Main conclusions
EHMOS could be used for a wide range of topics and extended to produce new insights, especially in climate change studies. Explicit estimation of optimum shifts notably allows investigation of ecological assumptions that could explain interspecific variability of these shifts.
